---
title: "Florida Breast Cancer Cases (2013 - 2017)"
subtitle: "Source: Florida Cancer Data System"
author:
- Office of Community Outreach, Engagement, & Equity
- McKenzie McIntyre
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: paged
---

```{r setup, echo=FALSE, eval=TRUE, include = FALSE}
.libPaths(c("C:/Temp/R/win-library", .libPaths()))
### Add packages needed here
packages = c('reactable', "knitr", "tidyverse", "dplyr", "readxl", "janitor", "fcds", "benford.analysis")

#if a package is installed, it will be loaded
#if any are not, the missing package(s) will be installed and loaded
package.check <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  }
  library(x, character.only = TRUE)
})

knitr::opts_chunk$set(comment = NA)

#load the recoded FCDS dataset
dat <- readRDS("G:/COEE/Data/FCDS Dataset 2020/R codes/datasets/fcds_dataset_2020_clean.rds")
#load the original FCDS dataset (for variables not included in the recoded version)
dat2 <- read.delim("G:/COEE/Data/FCDS Dataset 2020/DR 227/DR227 Dataset.dat", sep = ",", header = TRUE)

dat2 <- dat2 %>%
  mutate(
    dx_year = extract.digits(
      DATE_OF_DIAGNOSIS_N390,4)$data.digits,
    year_group = case_when( #count_fcds() uses variable year_group 
      dx_year %in% c("2008", "2009", "2010", "2011", "2012") ~ "2008-2012",
      dx_year %in% c("2013", "2014", "2015", "2016", "2017") ~ "2013-2017"),
    nodes = case_when(
      REGIONAL_NODES_POSITIVE_N820 >= 1 & REGIONAL_NODES_POSITIVE_N820 <4 ~ "1 to 3-Nodes",
      REGIONAL_NODES_POSITIVE_N820 >=4 & REGIONAL_NODES_POSITIVE_N820 <10 ~ "4 to 9-Nodes",
      REGIONAL_NODES_POSITIVE_N820 <9 & REGIONAL_NODES_POSITIVE_N820 <95 ~ "Above 9-Nodes"
      
    ))

dat2 <- dat2 %>% 
  mutate(
    treatment_c = case_when(
      between(RX_SUMM_CHEMO_N1390, 1, 3) ~ "Chemo"),
      treatment_h = case_when(RX_SUMM_HORMONE_N1400 == 01 ~ "Hormone"),
    treatment_i = case_when(RX_SUMM_BRM_N1410 == 01 ~ "Immune" ),
    treatment_r = case_when(
    between(RX_SUMM_RADIATION_N1360, 1, 5) ~ "Radiation"),
    treatment_s = case_when(
      RX_SUMM_SURG_PRIM_SITE_N1290 != 00 | RX_SUMM_SURG_PRIM_SITE_N1290 != 99 ~ "Primary Site Surgery")
    )

# dat2 <- dat2 %>% 
#   mutate(
#     treatment = case_when(
#       treatment_c == "Chemo" & treatment_i != "Immune" & treatment_h != "Hormone" & treatment_r != "Radiation" & treatment_s != "Primary Site Surgery" ~ "Chemo Only",
#       treatment_c != "Chemo" & treatment_i == "Immune" & treatment_h != "Hormone" & treatment_r != "Radiation" & treatment_s != "Primary Site Surgery" ~ "Immune Only",
#       treatment_c != "Chemo" & treatment_i != "Immune" & treatment_h == "Hormone" & treatment_r != "Radiation" & treatment_s != "Primary Site Surgery" ~ "Hormone Only",
#       treatment_c != "Chemo" & treatment_i != "Immune" & treatment_h != "Hormone" & treatment_r == "Radiation" & treatment_s != "Primary Site Surgery" ~ "Radiation Only",
#       treatment_c != "Chemo" & treatment_i != "Immune" & treatment_h != "Hormone" & treatment_r != "Radiation" & treatment_s == "Primary Site Surgery" ~ "Primary Site Surgery Only",
#       
#       
#       
#       treatment_c == "Chemo" & treatment_i == "Immune" & treatment_h != "Hormone" & treatment_r != "Radiation" & treatment_s != "Primary Site Surgery" ~ "Chemo and Immune",
#       treatment_c != "Chemo" & treatment_i == "Immune" & treatment_h != "Hormone" & treatment_r != "Radiation" & treatment_s != "Primary Site Surgery" ~ "Immune Only",
#       treatment_c != "Chemo" & treatment_i != "Immune" & treatment_h == "Hormone" & treatment_r != "Radiation" & treatment_s != "Primary Site Surgery" ~ "Hormone Only",
#       treatment_c != "Chemo" & treatment_i != "Immune" & treatment_h != "Hormone" & treatment_r == "Radiation" & treatment_s != "Primary Site Surgery" ~ "Radiation Only",
#       treatment_c != "Chemo" & treatment_i != "Immune" & treatment_h != "Hormone" & treatment_r != "Radiation" & treatment_s == "Primary Site Surgery" ~ "Primary Site Surgery Only",
#       
#     )
#   )

dat2 <- dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, year_group == "2013-2017") %>% 
  mutate(
    receptor_status = case_when(
    CS_SITE_SF_1_N2880 == 20 & CS_SITE_SF_2_N2890 == 20 & CS_SITE_SF15_N2869 == 20 ~ "ER(-), PR(-), HER2(-)",
    CS_SITE_SF_1_N2880 == 10 & CS_SITE_SF_2_N2890 == 20 & CS_SITE_SF15_N2869 == 20 ~ "ER(+), PR(-), HER2(-)",
    CS_SITE_SF_1_N2880 == 20 & CS_SITE_SF_2_N2890 == 10 & CS_SITE_SF15_N2869 == 20 ~ "ER(-), PR(+), HER2(-)",
    CS_SITE_SF_1_N2880 == 20 & CS_SITE_SF_2_N2890 == 20 & CS_SITE_SF15_N2869 == 10 ~ "ER(-), PR(-), HER2(+)",
    CS_SITE_SF_1_N2880 == 10 & CS_SITE_SF_2_N2890 == 10 & CS_SITE_SF15_N2869 == 20 ~ "ER(+), PR(+), HER2(-)",
    CS_SITE_SF_1_N2880 == 10 & CS_SITE_SF_2_N2890 == 20 & CS_SITE_SF15_N2869 == 10 ~ "ER(+), PR(-), HER2(+)",
    CS_SITE_SF_1_N2880 == 20 & CS_SITE_SF_2_N2890 == 10 & CS_SITE_SF15_N2869 == 10 ~ "ER(-), PR(+), HER2(+)",
    CS_SITE_SF_1_N2880 == 10 & CS_SITE_SF_2_N2890 == 10 & CS_SITE_SF15_N2869 == 10 ~ "ER(+), PR(+), HER2(+)"
    
  ))


##Apply filter on behavior 
# dat <- dat %>% filter(behavior == "Insitu")
dat0 <- dat2 %>% 
  mutate(
    behavior = case_when(
      BEHAVIOR_CODE_ICD_O_3_N523 == 2 ~ "Insitu",
      BEHAVIOR_CODE_ICD_O_3_N523 == 3 ~ "Invasive"
    )) %>% 
      filter(behavior == "Insitu" | behavior == "Invasive")
  
dat2 <- dat2 %>% filter(BEHAVIOR_CODE_ICD_O_3_N523 == 3)

##Apply filter on sequence number
#dat <- dat %>% filter(sequence_number == 0)
#dat2 <- dat2 %>% filter(SEQUENCE_NUMBER_CENTRAL_N380 == 0)
```


# Request 1 - AJCC Derived Variables{.tabset .tabset-fade .tabset-pills}
## Years 2013-2017
```{r, echo = FALSE}

cat("AJCC 7th Edition: T")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_N3400, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: T Description")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_DESCRIP_N3402, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_N3410, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N Description")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_DESCRIP_N3412, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_N3420, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M Description")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_DESCRIP_N3422, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: Stage Group")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_STAGE_GRP_N3430, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC Flag")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_FLAG_N3030, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()


cat("SS1977")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS1977_FLAG_N3040, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("SS2000")
dat0 %>%
  filter(year_group == "2013-2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS2000_FLAG_N3050, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

```


## Year: 2017
```{r, echo = FALSE}

cat("AJCC 7th Edition: T")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_N3400, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: T Description")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_DESCRIP_N3402, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_N3410, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N Description")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_DESCRIP_N3412, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_N3420, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M Description")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_DESCRIP_N3422, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: Stage Group")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_STAGE_GRP_N3430, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC Flag")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_FLAG_N3030, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()


cat("SS1977")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS1977_FLAG_N3040, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("SS2000")
dat0 %>%
  filter(dx_year == "2017", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS2000_FLAG_N3050, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

```


## Year: 2016
```{r, echo = FALSE}

cat("AJCC 7th Edition: T")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_N3400, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: T Description")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_DESCRIP_N3402, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_N3410, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N Description")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_DESCRIP_N3412, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_N3420, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M Description")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_DESCRIP_N3422, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: Stage Group")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_STAGE_GRP_N3430, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC Flag")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_FLAG_N3030, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()


cat("SS1977")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS1977_FLAG_N3040, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("SS2000")
dat0 %>%
  filter(dx_year == "2016", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS2000_FLAG_N3050, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

```

## Year: 2015
```{r, echo = FALSE}

cat("AJCC 7th Edition: T")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_N3400, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: T Description")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_DESCRIP_N3402, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_N3410, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N Description")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_DESCRIP_N3412, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_N3420, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M Description")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_DESCRIP_N3422, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: Stage Group")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_STAGE_GRP_N3430, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC Flag")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_FLAG_N3030, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()


cat("SS1977")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS1977_FLAG_N3040, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("SS2000")
dat0 %>%
  filter(dx_year == "2015", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS2000_FLAG_N3050, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

```

## Year: 2014
```{r, echo = FALSE}

cat("AJCC 7th Edition: T")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_N3400, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: T Description")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_DESCRIP_N3402, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_N3410, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N Description")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_DESCRIP_N3412, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_N3420, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M Description")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_DESCRIP_N3422, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: Stage Group")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_STAGE_GRP_N3430, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC Flag")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_FLAG_N3030, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()


cat("SS1977")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS1977_FLAG_N3040, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("SS2000")
dat0 %>%
  filter(dx_year == "2014", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS2000_FLAG_N3050, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

```


## Year: 2013
```{r, echo = FALSE}

cat("AJCC 7th Edition: T")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_N3400, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: T Description")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_T_DESCRIP_N3402, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_N3410, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: N Description")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_N_DESCRIP_N3412, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_N3420, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: M Description")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_M_DESCRIP_N3422, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC 7th Edition: Stage Group")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_7_STAGE_GRP_N3430, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("AJCC Flag")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_AJCC_FLAG_N3030, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()


cat("SS1977")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS1977_FLAG_N3040, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("SS2000")
dat0 %>%
  filter(dx_year == "2013", FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(DERIVED_SS2000_FLAG_N3050, behavior) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

```




# Request 2 - Prognostic and Staging Indicators - Invasive Cases {.tabset .tabset-fade .tabset-pills}
## Positive Regional Nodes: 1-3 
Receptor Type: ER, HER2, PR 0\
10: Positive\
20: Negative\
30: Equivocal\
998: Not done\
996/997/999: Unknown
```{r, echo = FALSE}

cat("Treatment: Chemo")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="1 to 3-Nodes", treatment_c=="Chemo") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Hormone")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="1 to 3-Nodes", treatment_h=="Hormone") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Immunotherapy")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="1 to 3-Nodes", treatment_i=="Immune") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Radiation")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="1 to 3-Nodes", treatment_r=="Radiation") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Primary Site Surgery")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="1 to 3-Nodes", treatment_s=="Primary Site Surgery") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()




```

## Positive Regional Nodes: 4-9
```{r, echo = FALSE}
cat("Treatment: Chemo")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="4 to 9-Nodes", treatment_c == "Chemo") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Hormone")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="4 to 9-Nodes", treatment_h=="Hormone") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Immunotherapy")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="4 to 9-Nodes", treatment_i=="Immune") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Radiation")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="4 to 9-Nodes", treatment_r=="Radiation") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Primary Site Surgery")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="4 to 9-Nodes", treatment_s=="Primary Site Surgery") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()
```

## Positive Regional Nodes: 9+
```{r, echo = FALSE}
cat("Treatment: Chemo")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="Above 9-Nodes", treatment_c=="Chemo") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Hormone")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="Above 9-Nodes", treatment_h=="Hormone") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Immunotherapy")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="Above 9-Nodes", treatment_i=="Immune") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Radiation")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="Above 9-Nodes", treatment_r=="Radiation") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()

cat("Treatment: Primary Site Surgery")
dat2 %>%
  filter(FCDS_SITE_GROUP_N2220 == 43, nodes=="Above 9-Nodes", treatment_s=="Primary Site Surgery") %>%
  janitor::tabyl(receptor_status, dx_year) %>%
  adorn_totals("row") %>%
  #adorn_pct_formatting() %>%
  knitr::kable()
```


## Tumor Grade by Receptor Status
1:	Grade I\
2:	Grade II\
3:	Grade III\
4:	Grade IV\
5:	T-cell\
6:	B-cell\
7:	Null cell\
8:	NK (natural killer) cell\
9:	Grade/differentiation unknown, not stated, or not applicable\
```{r, echo = FALSE}
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(receptor_status, GRADE_N440) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2013")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2013") %>%
  janitor::tabyl(receptor_status, GRADE_N440) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2014")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2014") %>%
  janitor::tabyl(receptor_status, GRADE_N440) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2015")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2015") %>%
  janitor::tabyl(receptor_status, GRADE_N440) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2016")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2016") %>%
  janitor::tabyl(receptor_status, GRADE_N440) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2017")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2017") %>%
  janitor::tabyl(receptor_status, GRADE_N440) %>% 
  adorn_totals("row") %>%
  knitr::kable()

```

## Tumor Size by Receptor Status
### The largest dimension or diameter of the primary tumor in millimeters
```{r, echo = FALSE}

dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43) %>%
  janitor::tabyl(CS_TUMOR_SIZE_N2800, receptor_status) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2013")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2013") %>%
  janitor::tabyl(CS_TUMOR_SIZE_N2800, receptor_status) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2014")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2014") %>%
  janitor::tabyl(CS_TUMOR_SIZE_N2800, receptor_status) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2015")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2015") %>%
  janitor::tabyl(CS_TUMOR_SIZE_N2800, receptor_status) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2016")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2016") %>%
  janitor::tabyl(CS_TUMOR_SIZE_N2800, receptor_status) %>% 
  adorn_totals("row") %>%
  knitr::kable()

cat("Diagnosis Year: 2017")
dat2 %>% 
  filter(FCDS_SITE_GROUP_N2220 == 43, dx_year=="2017") %>%
  janitor::tabyl(CS_TUMOR_SIZE_N2800, receptor_status) %>% 
  adorn_totals("row") %>%
  knitr::kable()

```
